Multiband Periodograms of Astronomical Sources

### 2014-12-12 writeup/paper.tex
add some example figures

\usepackage{url}
\usepackage{algorithmic,algorithm}
\usepackage{amssymb,amsmath}

@@

>>>>

\usepackage{url}
\usepackage{algorithmic,algorithm}
\usepackage{amssymb,amsmath}
\usepackage{graphicx}
\graphicspath{{figures/}}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig01.pdf}
  \caption{
    An illustration of the typical approach to multiband periodograms,
    in which each band is fit individually. The data consists of 60 coeval
    u-g-r-i-z observations spread over 180 nights, and is based on an
    RR Lyrae template from \citet{Sesar2010}. With this much data in each
    band, individual periodograms can be constructed and compared to find the
    true period $P=0.622$ days.
  }
  \label{fig:01}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig02.pdf}
  \caption{
    Another realization of the data from \fig{01}, with only a single-band
    observation each night (i.e. 12 observations per band, spread over 180
    days). In this case, there is not enough data in each band to recover
    periodicity information. By applying the multiband approach which utilizes
    all the data at once (lower right), we again see a significant spike of
    power at the true period $P=0.622$ days.    
  } 
  \label{fig:02}
\end{figure}
